Untitled

### 2025-02-24 script/discontinuity_w8.Rmd
import folders

setwd("~/Working paper/Trust/Script")
getwd()
```

@@

#ggsave("murdock_map.jpg", width = 10, height = 6, dpi = 300)

@@

# Get all objects in the current environment
all_objects <- ls()

# Determine which objects to remove
objects_to_remove <- setdiff(all_objects, objects_to_keep)

# Remove the unnecessary objects
rm(list = objects_to_remove)
```

@@

#ggsave("buffer_20.jpg", width = 10, height = 6, dpi = 300)

@@

# Get all objects in the current environment
all_objects <- ls()

# Determine which objects to remove
objects_to_remove <- setdiff(all_objects, objects_to_keep)

# Remove the unnecessary objects
rm(list = objects_to_remove)
```

```{r}
# Load data
data_trust_test <- readRDS("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_RDS/data_merge.rds")
bdd_geo <- read_csv("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/bdd_geo_w8.csv")

@@

# List of objects to keep
objects_to_keep <- c("df_list", "data_trust_test", "murdock_sf", "unions_list")

# Get all objects in the current environment
all_objects <- ls()

# Determine which objects to remove
objects_to_remove <- setdiff(all_objects, objects_to_keep)

# Remove the unnecessary objects
rm(list = objects_to_remove)
```

@@

# Prepare data
individuals <- data_trust_test %>%
  select(longitude, latitude, ISO) %>%
  na.omit()

capitals <- data_trust_test %>%
  select(caplong, caplat, ISO) %>%
  na.omit() %>%
  rename(longitude = caplong, latitude = caplat)

@@

selected_capitals <- capitals %>%
  filter(ISO%in% c("BEN", "BFA", "BWA", "CMR", "CIV", "GHA", "GIN", "KEN", "LBR", "MLI", "MWI", "MOZ", "NAM", "NER", "NGA", "SLE", "TZA", "UGA", "ZMB", "ZWE"))

# Plot
ggplot() +
  geom_sf(data = countries, fill = "white", color = "black") +
  theme_void() +
  geom_sf(data = selected_countries, fill = "green3", color = "black") +
    geom_point(data = selected_capitals, 
             aes(x = longitude, y = latitude), 
             size = 2, shape = 22, fill = "red", show.legend = FALSE)

#ggsave("writing/presentation/obs_map.jpg", width = 10, height = 10, units = "in", dpi = 300)

selected_countries <- countries %>% 
  filter(iso_a3 %in% c("BEN", "NER"))

selected_individuals <- individuals %>%
  filter(ISO%in% c("BEN", "NER"))

selected_capitals <- capitals %>%
  filter(ISO%in% c("BEN", "NER"))

test <- murdock_sf%>%
  distinct(NAME)

selected_murdock <- murdock_sf%>%
  filter(NAME=="DENDI")

@@

#test %<>%
  filter(ISO%in%c("BEN", "NER"))

@@

df_50 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(ISO) >= 2)%>%
  ungroup()

saveRDS(df_50, file="Data/Data_RDS/df_50_merge.rds")

write_dta(df_50, "Data/Data_dta/df_50_merge.dta")
```

@@

df_40 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(ISO) >= 2)%>%
  ungroup()

saveRDS(df_40, file="Data/Data_RDS/df_40_merge.rds")

write_dta(df_40, "Data/Data_dta/df_40_merge.dta")
```

@@

df_30 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(ISO) >= 2)%>%
  ungroup()

saveRDS(df_30, file="Data/Data_RDS/df_30_merge.rds")

write_dta(df_30, "Data/Data_dta/df_30_merge.dta")
```

@@

df_25 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(ISO) >= 2)%>%
  ungroup()

saveRDS(df_25, file="Data/Data_RDS/df_25_merge.rds")

write_dta(df_25, "Data/Data_dta/df_25_merge.dta")
```

@@

df_20 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(ISO) >= 2)%>%
  ungroup()

saveRDS(df_20, file="Data/Data_RDS/df_20_merge.rds")

write_dta(df_20, "Data/Data_dta/df_20_merge.dta")
```

@@

df_15 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(ISO) >= 2)%>%
  ungroup()

saveRDS(df_15, file="Data/Data_RDS/df_15_merge.rds")

write_dta(df_15, "Data/Data_dta/df_15_merge.dta")
```

@@

df_10 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(ISO) >= 2)%>%
  ungroup()

saveRDS(df_10, file="Data/Data_RDS/df_10_merge.rds")

write_dta(df_10, "Data/Data_dta/df_10_merge.dta")
```

>>>>

setwd("~/working_paper/trust/")
getwd()
```

@@

ggsave("plots/discontinuity/murdock_map.jpg", width = 10, height = 6, dpi = 300)

@@

# Get all objects in the current environment

# Determine which objects to remove

# Remove the unnecessary objects

```

@@

ggsave("buffer_20.jpg", width = 10, height = 6, dpi = 300)

@@

# Get all objects in the current environment

# Determine which objects to remove

# Remove the unnecessary objects

```

```{r}
# Load data
data_trust_test <- readRDS("data/data_rds/data_final_r.rds")
bdd_geo <- read_csv("data/data_raw/bdd_geo_w8.csv")

@@

# List of objects to keep
objects_to_keep <- c("df_list", "data_trust_test")

# Get all objects in the current environment

# Determine which objects to remove

# Remove the unnecessary objects

```

@@

# Prepare data
individuals <- data_trust_test %>%
  select(longitude, latitude, iso) %>%
  na.omit()

capitals <- data_trust_test %>%
  select(caplong, caplat, iso) %>%
  na.omit() %>%
  rename(longitude = caplong, latitude = caplat)

@@

selected_capitals <- capitals %>%
  filter(iso%in% c("BEN", "BFA", "BWA", "CMR", "CIV", "GHA", "GIN", "KEN", "LBR", "MLI", "MWI", "MOZ", "NAM", "NER", "NGA", "SLE", "TZA", "UGA", "ZMB", "ZWE"))

# Plot
ggplot() +
  geom_sf(data = countries, fill = "white", color = "black") +
  theme_void() +
  geom_sf(data = selected_countries, fill = "#E94849", color = "black") +
    geom_point(data = selected_capitals, 
             aes(x = longitude, y = latitude), 
             size = 2, shape = 22, fill = "black", show.legend = FALSE)

ggsave("plots/map/obs_map.jpg", width = 10, height = 10, units = "in", dpi = 300)

#selected_countries <- countries %>% 
 # filter(iso_a3 %in% c("BEN", "NER"))

#selected_individuals <- individuals %>%
 # filter(iso%in% c("BEN", "NER"))

#selected_capitals <- capitals %>%
 # filter(iso%in% c("BEN", "NER"))

#test <- murdock_sf%>%
#  distinct(NAME)

#selected_murdock <- murdock_sf%>%
#  filter(NAME=="DENDI")

@@

#test %<>%
 # filter(iso%in%c("BEN", "NER"))

@@

df_50$murdock_round <- paste0(df_50$murdock_names, df_50$round, sep="_")

df_50 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(iso) >= 2)%>%
  ungroup()

df_50 %<>%
  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))

saveRDS(df_50, file="data/data_rds/df_50.rds")

write_dta(df_50, "data/data_dta/df_50.dta")

df_50 %<>%
  group_by(murdock_round) %>%
  filter(n_distinct(iso) >= 2)%>%
ungroup()

df_50 %<>%
  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))

saveRDS(df_50, file="data/data_rds/df_50_2.rds")

write_dta(df_50, "data/data_dta/df_50_2.dta")

```

@@

df_40$murdock_round <- paste0(df_40$murdock_names, df_40$round, sep="_")

df_40 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(iso) >= 2)%>%
  ungroup()

df_40 %<>%
  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))

saveRDS(df_40, file="data/data_rds/df_40.rds")

write_dta(df_40, "data/data_dta/df_40.dta")

df_40 %<>%
  group_by(murdock_round) %>%
  filter(n_distinct(iso) >= 2)%>%
ungroup()

df_40 %<>%
  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))

saveRDS(df_40, file="data/data_rds/df_40_2.rds")

write_dta(df_40, "data/data_dta/df_40_2.dta")
```

@@

df_30$murdock_round <- paste0(df_30$murdock_names, df_30$round, sep="_")

df_30 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(iso) >= 2)%>%
  ungroup()

df_30 %<>%
  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))

saveRDS(df_30, file="data/data_rds/df_30.rds")
write_dta(df_30, "data/data_dta/df_30.dta")

df_30 %<>%
  group_by(murdock_round) %>%
  filter(n_distinct(iso) >= 2)%>%
ungroup()

df_30 %<>%
  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))

saveRDS(df_30, file="data/data_rds/df_30_2.rds")

write_dta(df_30, "data/data_dta/df_30_2.dta")

```

@@

df_25$murdock_round <- paste0(df_25$murdock_names, df_25$round, sep="_")

df_25 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(iso) >= 2)%>%
  ungroup()

df_25 %<>%
  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))

saveRDS(df_25, file="data/data_rds/df_25.rds")

write_dta(df_25, "data/data_dta/df_25.dta")

df_25 %<>%
  group_by(murdock_round) %>%
  filter(n_distinct(iso) >= 2)%>%
ungroup()

df_25 %<>%
  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))

saveRDS(df_25, file="data/data_rds/df_25_2.rds")

write_dta(df_25, "data/data_dta/df_25_2.dta")
```

@@

df_20$murdock_round <- paste0(df_20$murdock_names, df_20$round, sep="_")

df_20 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(iso) >= 2)%>%
  ungroup()

df_20 %<>%
  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))

saveRDS(df_20, file="data/data_rds/df_20.rds")

write_dta(df_20, "data/data_dta/df_20.dta")

df_20 %<>%
  group_by(murdock_round) %>%
  filter(n_distinct(iso) >= 2)%>%
ungroup()

df_20 %<>%
  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))

saveRDS(df_20, file="data/data_rds/df_20_2.rds")

write_dta(df_20, "data/data_dta/df_20_2.dta")
```

@@

df_15$murdock_round <- paste0(df_15$murdock_names, df_15$round, sep="_")

df_15 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(iso) >= 2)%>%
  ungroup()

df_15 %<>%
  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))

saveRDS(df_15, file="data/data_rds/df_15.rds")

write_dta(df_15, "data/data_dta/df_15.dta")

df_15 %<>%
  group_by(murdock_round) %>%
  filter(n_distinct(iso) >= 2)%>%
ungroup()

df_15 %<>%
  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))

saveRDS(df_15, file="data/data_rds/df_15_2.rds")

write_dta(df_15, "data/data_dta/df_15_2.dta")
```

@@

df_10$murdock_round <- paste0(df_10$murdock_names, df_10$round, sep="_")

df_10 %<>%
  group_by(murdock_names) %>%
  filter(n_distinct(iso) >= 2)%>%
  ungroup()

df_10 %<>%
  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))

saveRDS(df_10, file="data/data_rds/df_10.rds")

write_dta(df_10, "data/data_dta/df_10.dta")

df_10 %<>%
  group_by(murdock_round) %>%
  filter(n_distinct(iso) >= 2)%>%
ungroup()

df_10 %<>%
  mutate(cluster_bdd = as.numeric(factor(paste(region_time, murdock_names, sep = "_"))))

saveRDS(df_10, file="data/data_rds/df_10_2.rds")

write_dta(df_10, "data/data_dta/df_10_2.dta")
```
